---
title: "Untitled"
author: "Cheng Gao"
date: "3/17/2019"
output: html_document
---

```{r}
wd<- "/Users/chengg/Google Drive/EPICON/Mycobiome/Fungal ITS/statistic/Total.fungi"
setwd(wd)
library(ggplot2)
library(nlme)
library(MuMIn)
```


```{r, fig.height = 3, fig.width = 12, fig.align = "center"}
rm(list = ls())
load("EPICON.data.preparation.RC.bNTI.ghost.2019.03.17.Rdata")
col11<-c("#0000FF","#FF3399","#FFCC33","#ff00ff","#00ff00", "deepskyblue", "bisque",   "darkgreen","black", "maroon3",   "grey")
# bNTI.ghost2RC95pct.ghost
bNTI.ghost.RC.part.TP.TREAT$Treatment<-factor(bNTI.ghost.RC.part.TP.TREAT$Treatment, levels= c("Control", "Pre_flowering_drought", "Post_flowering_drought"), labels = c("CON", "PRE", "POST"))
bNTI.ghost.RC.part.TP.TREAT$Habitat<-factor(bNTI.ghost.RC.part.TP.TREAT$Habitat, levels= c("Leaf", "Root", "Rhizosphere", "Soil"), labels = c("Leaf", "Root", "Rhizo", "Soil"))
bNTI.ghost.RC.part.TP.TREAT$bNTI.ghost.RC.partition<-factor(bNTI.ghost.RC.part.TP.TREAT$bNTI.ghost.RC.partition,
                                                            labels = c("(-2, 2)   & [-1, -0.95)", "(-2, 2)   & (-0.95, 0.95)",  "(-2, 2)   & [0.95, 1)",   "[2, +∞)  & [0.95, 1)",  "[2, +∞)  & (-0.95, 0.95)"  ,  "[2, +∞)  & [-1, -0.95)" ,  "(+∞, -2] & [0.95, 1)" ,  "(+∞, -2] & (-0.95, 0.95)", "(+∞, -2] & [-1, -0.95)"))

ggplot(bNTI.ghost.RC.part.TP.TREAT[bNTI.ghost.RC.part.TP.TREAT$Treatment=="CON",], aes(x = factor(TP), y = Value ,fill=bNTI.ghost.RC.partition)) +
  geom_bar(stat='identity', position = "fill")+  ###add <   > for relative abundance
  labs(x="Week",y = "Relative importance")+
  facet_wrap(~Habitat, ncol = 4,strip.position= 'left')+
  theme(strip.text = element_text(size = 15,face="bold"),
        panel.spacing = unit(0, "lines"),
        legend.title = element_text(colour="black", size=15, face="bold"),
        legend.text = element_text(colour="black", size=15, face="bold"),
        axis.text=element_text(size=10,face="bold",angle = 90),
        axis.title=element_text(size=15,face="bold"))+
  scale_y_continuous(labels = scales::percent)+
  scale_fill_manual(values= col11) + guides(fill=FALSE)
```


```{r, fig.height = 5, fig.width = 15, fig.align = "center"}



#
rm(list = ls())
load("EPICON.data.preparation.RC.bNTI.ghost.2019.03.17.Rdata")
col11<-c("#0000FF","#FF3399","#FFCC33","#ff00ff","#00ff00", "deepskyblue", "bisque",   "darkgreen","black", "maroon3",   "grey")
# bNTI.ghost2RC95pct.ghost
bNTI.ghost.RC.part.TP.TREAT$Treatment<-factor(bNTI.ghost.RC.part.TP.TREAT$Treatment, levels= c("Control", "Pre_flowering_drought", "Post_flowering_drought"), labels = c("CON", "PRE", "POST"))
bNTI.ghost.RC.part.TP.TREAT$Habitat<-factor(bNTI.ghost.RC.part.TP.TREAT$Habitat, levels= c("Leaf", "Root", "Rhizosphere", "Soil"), labels = c("Leaf", "Root", "Rhizo", "Soil"))
bNTI.ghost.RC.part.TP.TREAT$bNTI.ghost.RC.partition<-factor(bNTI.ghost.RC.part.TP.TREAT$bNTI.ghost.RC.partition,
                                                            labels = c("(-2, 2)   & [-1, -0.95)", "(-2, 2)   & (-0.95, 0.95)",  "(-2, 2)   & [0.95, 1)",   "[2, +∞)  & [0.95, 1)",  "[2, +∞)  & (-0.95, 0.95)"  ,  "[2, +∞)  & [-1, -0.95)" ,  "(+∞, -2] & [0.95, 1)" ,  "(+∞, -2] & (-0.95, 0.95)", "(+∞, -2] & [-1, -0.95)"))
ggplot(bNTI.ghost.RC.part.TP.TREAT, aes(x = factor(TP), y = Value ,fill=bNTI.ghost.RC.partition)) +
  geom_bar(stat='identity', position = "fill")+  ###add <   > for relative abundance
  labs(x="Week",y = "Relative importance")+
  facet_grid(Treatment~Habitat)+
  labs(fill="       βNTI   &   RCI")+
  theme(strip.text = element_text(size = 15,face="bold"),
        panel.spacing = unit(0, "lines"),
        legend.title = element_text(colour="black", size=15, face="bold"),
        legend.text = element_text(colour="black", size=15, face="bold"),
        axis.text=element_text(size=10,face="bold",angle = 90),
        axis.title=element_text(size=15,face="bold"))+
  scale_y_continuous(labels = scales::percent)+
  scale_fill_manual(values= col11) 

ggplot(bNTI.ghost.RC.part.TP.TREAT, aes(x = factor(TP), y = Value ,fill=bNTI.ghost.RC.partition)) +
  geom_bar(stat='identity', position = "fill")+  ###add <   > for relative abundance
  labs(x="Week",y = "Relative importance")+
 facet_grid(Treatment~Habitat)+
  theme(strip.text = element_text(size = 15,face="bold"),
        panel.spacing = unit(0, "lines"),
        legend.title = element_text(colour="black", size=15, face="bold"),
        legend.text = element_text(colour="black", size=15, face="bold"),
        axis.text=element_text(size=10,face="bold",angle = 90),
        axis.title=element_text(size=15,face="bold"))+
  scale_y_continuous(labels = scales::percent)+
  scale_fill_manual(values= col11) + guides(fill=FALSE)

######RCI alone
rm(list = ls())
load("EPICON.data.preparation.RC.bNTI.ghost.2019.03.17.Rdata")
col11<-c("#0000FF","#FF3399","#FFCC33","#ff00ff","#00ff00", "deepskyblue", "bisque",   "darkgreen","black", "maroon3",   "grey")

RC.part.TP.TREAT$Treatment<-factor(RC.part.TP.TREAT$Treatment, levels= c("Control", "Pre_flowering_drought", "Post_flowering_drought"), labels = c("CON", "PRE", "POST"))
RC.part.TP.TREAT$Habitat<-factor(RC.part.TP.TREAT$Habitat, levels= c("Leaf", "Root", "Rhizosphere", "Soil"), labels = c("Leaf", "Root", "Rhizo", "Soil"))
RC.part.TP.TREAT$RC.partition<-factor(RC.part.TP.TREAT$RC.partition,
                                      labels = c("[-1, -0.95]", "(-0.95, 0.95)", "[0.95, 1]"))

ggplot(RC.part.TP.TREAT, aes(x = factor(TP), y = Value ,fill=RC.partition)) +
  geom_bar(stat='identity', position = "fill")+  ###add <   > for relative abundance
  labs(x="Week",y = "Relative importance")+
 facet_grid(Treatment~Habitat)+
  labs(fill="       RCI")+
  theme(strip.text = element_text(size = 15,face="bold"),
        panel.spacing = unit(0, "lines"),
        legend.title = element_text(colour="black", size=15, face="bold"),
        legend.text = element_text(colour="black", size=15, face="bold"),
        axis.text=element_text(size=10,face="bold",angle = 90),
        axis.title=element_text(size=15,face="bold"))+
  scale_y_continuous(labels = scales::percent)+
  scale_fill_manual(values= col11) 


ggplot(RC.part.TP.TREAT, aes(x = factor(TP), y = Value ,fill=RC.partition)) +
  geom_bar(stat='identity', position = "fill")+  ###add <   > for relative abundance
  labs(x="Week",y = "Relative importance")+
 facet_grid(Treatment~Habitat)+
  theme(strip.text = element_text(size = 15,face="bold"),
        panel.spacing = unit(0, "lines"),
        legend.title = element_text(colour="black", size=15, face="bold"),
        legend.text = element_text(colour="black", size=15, face="bold"),
        axis.text=element_text(size=10,face="bold",angle = 90),
        axis.title=element_text(size=15,face="bold"))+
  scale_y_continuous(labels = scales::percent)+
  scale_fill_manual(values= col11) + guides(fill=FALSE)

#####
rm(list = ls())
load("EPICON.data.preparation.RC.bNTI.its2.2019.03.17.Rdata")
col11<-c("#0000FF","#FF3399","#FFCC33","#ff00ff","#00ff00","deepskyblue", "bisque",   "darkgreen","black", "maroon3",   "grey")
# bNTI.its22RC95pct
bNTI.its2.RC.part.TP.TREAT$Treatment<-factor(bNTI.its2.RC.part.TP.TREAT$Treatment, levels= c("Control", "Pre_flowering_drought", "Post_flowering_drought"), labels = c("CON", "PRE", "POST"))
bNTI.its2.RC.part.TP.TREAT$Habitat<-factor(bNTI.its2.RC.part.TP.TREAT$Habitat, levels= c("Leaf", "Root", "Rhizosphere", "Soil"), labels = c("Leaf", "Root", "Rhizo", "Soil"))
bNTI.its2.RC.part.TP.TREAT$bNTI.its2.RC.partition<-factor(bNTI.its2.RC.part.TP.TREAT$bNTI.its2.RC.partition,
                                                            labels = c("(-2, 2)   & [-1, -0.95)", "(-2, 2)   & (-0.95, 0.95)",  "(-2, 2)   & [0.95, 1)",   "[2, +∞)  & [0.95, 1)",  "[2, +∞)  & (-0.95, 0.95)"  ,  "[2, +∞)  & [-1, -0.95)" ,  "(+∞, -2] & [0.95, 1)" ,  "(+∞, -2] & (-0.95, 0.95)", "(+∞, -2] & [-1, -0.95)"))
ggplot(bNTI.its2.RC.part.TP.TREAT, aes(x = factor(TP), y = Value ,fill=bNTI.its2.RC.partition)) +
  geom_bar(stat='identity', position = "fill")+  ###add <   > for relative abundance
  labs(x="Week",y = "Relative importance")+
 facet_grid(Treatment~Habitat)+
  labs(fill="       βNTI   &   RCI")+
  theme(strip.text = element_text(size = 15,face="bold"),
        panel.spacing = unit(0, "lines"),
        legend.title = element_text(colour="black", size=15, face="bold"),
        legend.text = element_text(colour="black", size=15, face="bold"),
        axis.text=element_text(size=10,face="bold",angle = 90),
        axis.title=element_text(size=15,face="bold"))+
  scale_y_continuous(labels = scales::percent)+
  scale_fill_manual(values= col11) 

ggplot(bNTI.its2.RC.part.TP.TREAT, aes(x = factor(TP), y = Value ,fill=bNTI.its2.RC.partition)) +
  geom_bar(stat='identity', position = "fill")+  ###add <   > for relative abundance
  labs(x="Week",y = "Relative importance")+
 facet_grid(Treatment~Habitat)+
  theme(strip.text = element_text(size = 15,face="bold"),
        panel.spacing = unit(0, "lines"),
        legend.title = element_text(colour="black", size=15, face="bold"),
        legend.text = element_text(colour="black", size=15, face="bold"),
        axis.text=element_text(size=10,face="bold",angle = 90),
        axis.title=element_text(size=15,face="bold"))+
  scale_y_continuous(labels = scales::percent)+
  scale_fill_manual(values= col11) + guides(fill=FALSE)
```


```{r, fig.height = 3, fig.width = 4, fig.align = "center"}
rm(list = ls())
rm(list = ls())

load("EPICON.data.preparation.RC.bNTI.its2.2019.03.17.Rdata")

# RC95
ggplot(data=Lagg, aes(y=RC95pct, x= Fungi.pct/100, color=Habitat))+
  geom_smooth( method="loess", span=0.9)+ geom_point() + theme_bw()+
  xlab("Fungal amplicon %")+ylab("|RCI|< 0.95")+
  scale_y_continuous(labels = scales::percent)+
  scale_x_continuous(labels = scales::percent)+
  theme(axis.text=element_text(size=10,face="bold"),
        axis.title=element_text(size=14,face="bold"))+ theme(legend.position = "none")
lme0<-lme(RC95pct~Fungi.pct,random=~1|Habitat,data=Lagg)
summary(lme0)
anova(lme0)
r.squaredGLMM(lme0)

ggplot(data=Traagg, aes(y=RC95pct, x= log(Fungi.pct.tra) , color=Habitat) )+
  geom_smooth( method="loess", span=0.9)+ geom_point() + theme_bw()+
  xlab("Log(fungal transcription%)")+ylab("|RCI| < 0.95")+
  scale_y_continuous(labels = scales::percent)+
  theme(axis.text=element_text(size=10,face="bold"),
        axis.title=element_text(size=14,face="bold"))+ theme(legend.position = "none")
lme0<-lme(RC95pct~log(Fungi.pct.tra),random=~1|Habitat,data=Traagg)
summary(lme0)
anova(lme0)
r.squaredGLMM(lme0)

ggplot(data=LaggqPCR, aes(y=RC95pct, x= qPCR , color=Habitat) )+
  geom_smooth( method="loess", span=0.9)+ geom_point() + theme_bw()+
  xlab("SSU qPCR")+ylab("|RCI| < 0.95")+
  scale_y_continuous(labels = scales::percent)+
  theme(axis.text=element_text(size=10,face="bold"),
        axis.title=element_text(size=14,face="bold"))+ theme(legend.position = "none")
lme0<-lme(RC95pct~qPCR,random=~1|Habitat,data=LaggqPCR)
summary(lme0)
anova(lme0)
r.squaredGLMM(lme0)

ggplot(data=Lagg, aes(y=RC95pct, x= S.rar362, color = Habitat) )+
  geom_smooth( method="loess", span = 0.9)+ geom_point() + theme_bw()+
  xlab("Richness")+ylab("|RCI| < 0.95")+
  scale_y_continuous(labels = scales::percent)+
  theme(axis.text=element_text(size=10,face="bold"),
        axis.title=element_text(size=14,face="bold"))+ theme(legend.position = "none")
lme0<-lme(RC95pct~S.rar362,random=~1|Habitat,data=Lagg)
summary(lme0)
anova(lme0)
r.squaredGLMM(lme0)






#####RC.bNTI.its2
ggplot(data=Lagg, aes(y=bNTI.its22RC95pct, x= Fungi.pct/100, color=Habitat))+
  geom_smooth( method="loess", span=0.9)+ geom_point() + theme_bw()+
  xlab("Fungal amplicon %")+ylab("|βNTI.its2|< 2 & |RCI| < 0.95")+
  scale_y_continuous(labels = scales::percent)+
  scale_x_continuous(labels = scales::percent)+
  theme(axis.text=element_text(size=10,face="bold"),
        axis.title=element_text(size=14,face="bold"))+ theme(legend.position = "none")
lme0<-lme(bNTI.its22RC95pct~Fungi.pct,random=~1|Habitat,data=Lagg)
summary(lme0)
anova(lme0)
r.squaredGLMM(lme0)

ggplot(data=Traagg, aes(y=bNTI.its22RC95pct, x= log(Fungi.pct.tra) , color=Habitat) )+
  geom_smooth( method="loess", span=0.9)+ geom_point() + theme_bw()+
  xlab("Log(fungal transcription%)")+ylab("|βNTI.its2|< 2 & |RCI| < 0.95")+
  scale_y_continuous(labels = scales::percent)+
  theme(axis.text=element_text(size=10,face="bold"),
        axis.title=element_text(size=14,face="bold"))+ theme(legend.position = "none")
lme0<-lme(bNTI.its22RC95pct~log(Fungi.pct.tra),random=~1|Habitat,data=Traagg)
summary(lme0)
anova(lme0)
r.squaredGLMM(lme0)

ggplot(data=LaggqPCR, aes(y=bNTI.its22RC95pct, x= qPCR , color=Habitat) )+
  geom_smooth( method="loess", span=0.9)+ geom_point() + theme_bw()+
  xlab("SSU qPCR")+ylab("|βNTI.its2|< 2 & |RCI| < 0.95")+
  scale_y_continuous(labels = scales::percent)+
  theme(axis.text=element_text(size=10,face="bold"),
        axis.title=element_text(size=14,face="bold"))+ theme(legend.position = "none")
lme0<-lme(bNTI.its22RC95pct~qPCR,random=~1|Habitat,data=LaggqPCR)
summary(lme0)
anova(lme0)
r.squaredGLMM(lme0)

ggplot(data=Lagg, aes(y=bNTI.its22RC95pct, x= S.rar362, color = Habitat) )+
  geom_smooth( method="loess", span = 0.9)+ geom_point() + theme_bw()+
  xlab("Richness")+ylab("|βNTI.its2|< 2 & |RCI| < 0.95")+
  scale_y_continuous(labels = scales::percent)+
  theme(axis.text=element_text(size=10,face="bold"),
        axis.title=element_text(size=14,face="bold"))+ theme(legend.position = "none")
lme0<-lme(bNTI.its22RC95pct~S.rar362,random=~1|Habitat,data=Lagg)
summary(lme0)
anova(lme0)
r.squaredGLMM(lme0)


##### RC.bNTI.ghost
rm(list = ls())
rm(list = ls())

load("EPICON.data.preparation.RC.bNTI.ghost.2019.03.17.Rdata")

ggplot(data=Lagg, aes(y=bNTI.ghost2RC95pct, x= Fungi.pct/100, color=Habitat))+
  geom_smooth( method="loess", span=0.9)+ geom_point() + theme_bw()+
  xlab("Fungal amplicon %")+ylab("|βNTI.gt|< 2 & |RCI| < 0.95")+
  scale_y_continuous(labels = scales::percent)+
  scale_x_continuous(labels = scales::percent)+
  theme(axis.text=element_text(size=10,face="bold"),
        axis.title=element_text(size=14,face="bold"))+ theme(legend.position = "none")
lme0<-lme(bNTI.ghost2RC95pct~Fungi.pct,random=~1|Habitat,data=Lagg)
summary(lme0)
anova(lme0)
r.squaredGLMM(lme0)

ggplot(data=Traagg, aes(y=bNTI.ghost2RC95pct, x= log(Fungi.pct.tra) , color=Habitat) )+
  geom_smooth( method="loess", span=0.9)+ geom_point() + theme_bw()+
  xlab("Log(fungal transcription%)")+ylab("|βNTI.gt|< 2 & |RCI| < 0.95")+
  scale_y_continuous(labels = scales::percent)+
  theme(axis.text=element_text(size=10,face="bold"),
        axis.title=element_text(size=14,face="bold"))+ theme(legend.position = "none")
lme0<-lme(bNTI.ghost2RC95pct~log(Fungi.pct.tra),random=~1|Habitat,data=Traagg)
summary(lme0)
anova(lme0)
r.squaredGLMM(lme0)

ggplot(data=LaggqPCR, aes(y=bNTI.ghost2RC95pct, x= qPCR , color=Habitat) )+
  geom_smooth( method="loess", span=0.9)+ geom_point() + theme_bw()+
  xlab("SSU qPCR")+ylab("|βNTI.gt|< 2 & |RCI| < 0.95")+
  scale_y_continuous(labels = scales::percent)+
  theme(axis.text=element_text(size=10,face="bold"),
        axis.title=element_text(size=14,face="bold"))+ theme(legend.position = "none")
lme0<-lme(bNTI.ghost2RC95pct~qPCR,random=~1|Habitat,data=LaggqPCR)
summary(lme0)
anova(lme0)
r.squaredGLMM(lme0)

ggplot(data=Lagg, aes(y=bNTI.ghost2RC95pct, x= S.rar362, color = Habitat) )+
  geom_smooth( method="loess", span = 0.9)+ geom_point() + theme_bw()+
  xlab("Richness")+ylab("|βNTI.gt|< 2 & |RCI| < 0.95")+
  scale_y_continuous(labels = scales::percent)+
  theme(axis.text=element_text(size=10,face="bold"),
        axis.title=element_text(size=14,face="bold"))+ theme(legend.position = "none")
lme0<-lme(bNTI.ghost2RC95pct~S.rar362,random=~1|Habitat,data=Lagg)
summary(lme0)
anova(lme0)
r.squaredGLMM(lme0)

```


######DATA PREPARATION RC BNTI ITS2#####

setwd("/Users/chengg/Google Drive/EPICON/Mycobiome/Fungal ITS/statistic/Total.fungi")
library(reshape2)
library(ggplot2)
library(MASS)
library(splitstackshape)
library(colorRamps)
library(vegan)
library(betapart)
library(ape)
library(DOC)
library(ecodist)
library(gridExtra)
library(nlme)
library(MuMIn)
source("weighted Fst function.r")
env0<-read.csv("epicon.ENV.2017.12.05.csv", head = T)
fung0<-read.csv("epicon.ID.mat.2018.06.12.csv", head=T, row.names =1) ##Read in the raw data###

gr<-fung0$Fungi=="Fungi"
#gr<-fung0$Phylum=="Basidiomycota"

fungt<-data.frame(fung0[gr ,c(1:1251) ]) ### raw data of all samples including pseudo samples #
ID<-data.frame(fung0[gr ,c(-1:-1251) ]) ### raw data of all samples including pseudo samples #
ID1<-data.frame(rownames(ID),ID$Phylum_lifestyle, ID$Phylum)
#names(ID1)<- c("ID", "Phylum_lifestyle", "Phylum", "Life_style")
#Flev<-ID$Phylum
#Flev<-ID$Phylum_lifestyle
Flev<-rownames(ID);
taxonomy<-data.frame(ID$Kingdom,ID$Phylum.ab, ID$Class.ab, ID$Order, ID$Family, ID$Genus);
colnames(taxonomy) = c("kingdom","phylum","class","order","family","genus");
rownames(taxonomy)<-rownames(ID)
fung.lev<-data.frame(aggregate(fungt,by=list(Flev) , sum))
rownames(fung.lev)<-fung.lev[,1]; fung.lev<-fung.lev[match(Flev, fung.lev$Group.1),]
fung.lev<-fung.lev[,-1]
fung1<-data.frame(t(fung.lev))

fung.raw.pseudo<-fung1[env0$Habitat!="Prop_root",]  # can be useful for Barplots of total fungi
env.F.raw.pseudo<-env0[env0$Habitat!="Prop_root",]   # can be useful for Barplots of total fungi

fung.raw<-fung.raw.pseudo[c(1:1026),] ### raw data of all samples #
env.raw<-env.F.raw.pseudo[c(1:1026),]

cutoff<-362 # the cutoff for rarefaction

fung.rar<-data.frame(rrarefy(fung.raw, cutoff))   
env<-env.raw[rowSums(fung.rar)==cutoff,]
fung<-fung.rar[rowSums(fung.rar)==cutoff,colSums(fung.rar)>0]
fung<-fung[,colSums(fung)>0]

# bNTI.its2
phylo = read.tree("EPICON.fungi.tree.txt");
#phylo; # a summary of the phylogeny
#plot.phylo(phylo,typ="fan", font =1, cex=1)
bNTI.its2<-read.csv("weighted_bNTI.its2.F.csv", head = T, row.names =1)
bNTI.its2<-as.dist(bNTI.its2)
bNTI.its201<-(bNTI.its2-min(bNTI.its2))/(max(bNTI.its2)-min(bNTI.its2))

#RC
rc0<-read.csv("rc.RSZL.F.csv", head = T, row.names =1)
rc<-as.dist(rc0)
rc01<-(rc+1)/2

env.L<-env
fungL.R362F<-fung
tmp<-fung ## abudance data

tmp01<-tmp
tmp01[tmp01>0]=1      # 0 1 data
env.L$S.rar362<-specnumber(fungL.R362F)
env.L$H.rar362<-vegan::diversity(fungL.R362F)
env.L$J.rar362<-env.L$H.rar362/log(env.L$S.rar362)
env.L$TP1[env.L$TP>7]="Weeks8_17" ; env.L$TP1[env.L$TP<8]="Weeks1_7" # to divide all time points to early and later groups
env.L$bb<-droplevels(interaction( env.L$Timepiont,env.L$Habitat,env.L$Treatment1,sep = "."))
env.L$Habitat2<-factor(droplevels(env.L$Habitat), levels=c("Leaf", "Root", "Rhizosphere", "Soil"),
                       labels = c("L", "R", "Z", "S"))
env.L$aa1<-paste("TP",env.L$TP, env.L$Habitat2,env.L$plot, sep = "")

env.L$va<-interaction(env.L$TP, env.L$Habitat2)

phylo = read.tree("EPICON.fungi.tree.txt");
#phylo; # a summary of the phylogeny
#plot.phylo(phylo,typ="fan", font =1, cex=1)
bNTI.its2<-read.csv("weighted_bNTI.its2.F.csv", head = T, row.names =1)
bNTI.its2<-as.dist(bNTI.its2)
bNTI.its201<-(bNTI.its2-min(bNTI.its2))/(max(bNTI.its2)-min(bNTI.its2))

#RC
rc0<-read.csv("rc.RSZL.F.csv", head = T, row.names =1)
rc<-as.dist(rc0)
rc01<-(rc+1)/2

env.L$va<-interaction(env.L$TP, env.L$Habitat2)
fd<-beta.pair(tmp01, index.family = "jaccard")
bc<-vegdist(tmp)
bd.rc<-betadisper(rc01,env.L$va)
env.L$RCdisper<-bd.rc$distances
bd.bc<-betadisper(bc,env.L$va)
env.L$bradisper<-bd.bc$distances
bd.jac<-betadisper(fd$beta.jac,env.L$va)
env.L$jacdisper<-bd.jac$distances
bd.jne<-betadisper(fd$beta.jne,env.L$va)
env.L$jnedisper<-bd.jne$distances
bd.jtu<-betadisper(fd$beta.jtu,env.L$va)
env.L$jtudisper<-bd.jtu$distances
bd.bNTI.its201<-betadisper(bNTI.its201,env.L$va)
env.L$bNTI.its2disper<-bd.bNTI.its201$distances

###################################### 
# Transcriptome samples level metrics#
######################################

Tra<-read.csv("LR.mycotranscriptome.csv", head = T)

env.Tra<- merge(Tra,env.L, by.x="aa", by.y="aa1", all =FALSE)
env.Tra$Pct.Tra<-rowSums(env.Tra[,c(12:20,22:24)])/env.Tra$FilteredReads
tmp.Tra<-tmp[rownames(tmp) %in% env.Tra$aa,]
tmp.Tra<-tmp.Tra[colSums(tmp.Tra)>0] ## abudance data
tmp.Tra01<-tmp.Tra
tmp.Tra01[tmp.Tra01>0]=1 

###################################### 
# Metabolome samples level metrics#
######################################

Met<-read.csv("EPICON.metabolome.csv", head = T)
env.Tra.Met<-env.Tra[env.Tra$aa %in% Met$aa,]
Met1<-Met[Met$aa %in% env.Tra.Met$aa,]
tmp.Tra.Met<-tmp.Tra[rownames(tmp.Tra) %in% env.Tra.Met$aa,]## abudance data
tmp.Tra.Met01<-tmp.Tra.Met
tmp.Tra.Met01[tmp.Tra.Met01>0]=1 

##############################################
## To aggarete variables by TP.TREAT##
##############################################

bNTI.its2<-read.csv("weighted_bNTI.its2.S.F.csv", head = T, row.names =1)
bNTI.its2<-as.dist(bNTI.its2)
bNTI.its2.01<-(bNTI.its2-min(bNTI.its2))/(max(bNTI.its2)-min(bNTI.its2))

rc0<-read.csv("rc.S.F.csv", head = T, row.names =1)
rc<-as.dist(rc0)
rc.01<-(rc+1)/2

env.L1<-droplevels(env.L[env.L$Habitat=="Soil",])

t1<-levels(env.L1$bb)
LbNTI.its2 = NULL
for (i in t1){
  m1<-as.matrix(bNTI.its2)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  LbNTI.its2<-rbind(LbNTI.its2,m1)
}
LbNTI.its22<-cSplit(LbNTI.its2, "TP.TREAT", ".")
LbNTI.its22$TP.TREAT_1<-as.numeric(gsub("TP", "" , LbNTI.its22$TP.TREAT_1))
LbNTI.its2.TP.TREAT<-LbNTI.its22
names(LbNTI.its2.TP.TREAT)<-c("bNTI.its2", "TP","Habitat", "Treatment")
LbNTI.its2<-data.frame(LbNTI.its2$TP.TREAT,LbNTI.its2.TP.TREAT)
names(LbNTI.its2)<-c("TP.TREAT", "bNTI.its2", "TP","Habitat", "Treatment")
# RC
t1<-levels(env.L1$bb)
Lrc = NULL
for (i in t1){
  m1<-as.matrix(rc)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  Lrc<-rbind(Lrc,m1)
}
Lrc2<-cSplit(Lrc, "TP.TREAT", ".")
Lrc2$TP.TREAT_1<-as.numeric(gsub("TP", "" , Lrc2$TP.TREAT_1))
RC.TP.TREAT<-Lrc2
names(RC.TP.TREAT)<-c("RC", "TP","Habitat", "Treatment")
Lrc<-data.frame(Lrc$TP.TREAT,Lrc2)
names(Lrc)<-c("TP.TREAT", "RC", "TP","Habitat", "Treatment")
LbNTI.its2.S<-LbNTI.its2
Lrc.S<-Lrc

#
bNTI.its2<-read.csv("weighted_bNTI.its2.Z.F.csv", head = T, row.names =1)
bNTI.its2<-as.dist(bNTI.its2)
bNTI.its2.01<-(bNTI.its2-min(bNTI.its2))/(max(bNTI.its2)-min(bNTI.its2))

rc0<-read.csv("rc.Z.F.csv", head = T, row.names =1)
rc<-as.dist(rc0)
rc.01<-(rc+1)/2

env.L1<-droplevels(env.L[env.L$Habitat=="Rhizosphere",])

t1<-levels(env.L1$bb)
LbNTI.its2 = NULL
for (i in t1){
  m1<-as.matrix(bNTI.its2)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  LbNTI.its2<-rbind(LbNTI.its2,m1)
}
LbNTI.its22<-cSplit(LbNTI.its2, "TP.TREAT", ".")
LbNTI.its22$TP.TREAT_1<-as.numeric(gsub("TP", "" , LbNTI.its22$TP.TREAT_1))
LbNTI.its2.TP.TREAT<-LbNTI.its22
names(LbNTI.its2.TP.TREAT)<-c("bNTI.its2", "TP","Habitat", "Treatment")
LbNTI.its2<-data.frame(LbNTI.its2$TP.TREAT,LbNTI.its2.TP.TREAT)
names(LbNTI.its2)<-c("TP.TREAT", "bNTI.its2", "TP","Habitat", "Treatment")
# RC
t1<-levels(env.L1$bb)
Lrc = NULL
for (i in t1){
  m1<-as.matrix(rc)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  Lrc<-rbind(Lrc,m1)
}
Lrc2<-cSplit(Lrc, "TP.TREAT", ".")
Lrc2$TP.TREAT_1<-as.numeric(gsub("TP", "" , Lrc2$TP.TREAT_1))
RC.TP.TREAT<-Lrc2
names(RC.TP.TREAT)<-c("RC", "TP","Habitat", "Treatment")
Lrc<-data.frame(Lrc$TP.TREAT,Lrc2)
names(Lrc)<-c("TP.TREAT", "RC", "TP","Habitat", "Treatment")
LbNTI.its2.Z<-LbNTI.its2
Lrc.Z<-Lrc

#
bNTI.its2<-read.csv("weighted_bNTI.its2.R.F.csv", head = T, row.names =1)
bNTI.its2<-as.dist(bNTI.its2)
bNTI.its2.01<-(bNTI.its2-min(bNTI.its2))/(max(bNTI.its2)-min(bNTI.its2))

rc0<-read.csv("rc.R.F.csv", head = T, row.names =1)
rc<-as.dist(rc0)
rc.01<-(rc+1)/2

env.L1<-droplevels(env.L[env.L$Habitat=="Root",])

t1<-levels(env.L1$bb)
LbNTI.its2 = NULL
for (i in t1){
  m1<-as.matrix(bNTI.its2)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  LbNTI.its2<-rbind(LbNTI.its2,m1)
}
LbNTI.its22<-cSplit(LbNTI.its2, "TP.TREAT", ".")
LbNTI.its22$TP.TREAT_1<-as.numeric(gsub("TP", "" , LbNTI.its22$TP.TREAT_1))
LbNTI.its2.TP.TREAT<-LbNTI.its22
names(LbNTI.its2.TP.TREAT)<-c("bNTI.its2", "TP","Habitat", "Treatment")
LbNTI.its2<-data.frame(LbNTI.its2$TP.TREAT,LbNTI.its2.TP.TREAT)
names(LbNTI.its2)<-c("TP.TREAT", "bNTI.its2", "TP","Habitat", "Treatment")
# RC
t1<-levels(env.L1$bb)
Lrc = NULL
for (i in t1){
  m1<-as.matrix(rc)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  Lrc<-rbind(Lrc,m1)
}
Lrc2<-cSplit(Lrc, "TP.TREAT", ".")
Lrc2$TP.TREAT_1<-as.numeric(gsub("TP", "" , Lrc2$TP.TREAT_1))
RC.TP.TREAT<-Lrc2
names(RC.TP.TREAT)<-c("RC", "TP","Habitat", "Treatment")
Lrc<-data.frame(Lrc$TP.TREAT,Lrc2)
names(Lrc)<-c("TP.TREAT", "RC", "TP","Habitat", "Treatment")
LbNTI.its2.R<-LbNTI.its2
Lrc.R<-Lrc

#
bNTI.its2<-read.csv("weighted_bNTI.its2.L.F.csv", head = T, row.names =1)
bNTI.its2<-as.dist(bNTI.its2)
bNTI.its2.01<-(bNTI.its2-min(bNTI.its2))/(max(bNTI.its2)-min(bNTI.its2))

rc0<-read.csv("rc.L.F.csv", head = T, row.names =1)
rc<-as.dist(rc0)
rc.01<-(rc+1)/2

env.L1<-droplevels(env.L[env.L$Habitat=="Leaf",])

t1<-levels(env.L1$bb)
LbNTI.its2 = NULL
for (i in t1){
  m1<-as.matrix(bNTI.its2)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  LbNTI.its2<-rbind(LbNTI.its2,m1)
}
LbNTI.its22<-cSplit(LbNTI.its2, "TP.TREAT", ".")
LbNTI.its22$TP.TREAT_1<-as.numeric(gsub("TP", "" , LbNTI.its22$TP.TREAT_1))
LbNTI.its2.TP.TREAT<-LbNTI.its22
names(LbNTI.its2.TP.TREAT)<-c("bNTI.its2", "TP","Habitat", "Treatment")
LbNTI.its2<-data.frame(LbNTI.its2$TP.TREAT,LbNTI.its2.TP.TREAT)
names(LbNTI.its2)<-c("TP.TREAT", "bNTI.its2", "TP","Habitat", "Treatment")
# RC
t1<-levels(env.L1$bb)
Lrc = NULL
for (i in t1){
  m1<-as.matrix(rc)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  Lrc<-rbind(Lrc,m1)
}
Lrc2<-cSplit(Lrc, "TP.TREAT", ".")
Lrc2$TP.TREAT_1<-as.numeric(gsub("TP", "" , Lrc2$TP.TREAT_1))
RC.TP.TREAT<-Lrc2
names(RC.TP.TREAT)<-c("RC", "TP","Habitat", "Treatment")
Lrc<-data.frame(Lrc$TP.TREAT,Lrc2)
names(Lrc)<-c("TP.TREAT", "RC", "TP","Habitat", "Treatment")

LbNTI.its2.L<-LbNTI.its2
Lrc.L<-Lrc

LbNTI.its2<-rbind(LbNTI.its2.L , LbNTI.its2.Z, LbNTI.its2.R,LbNTI.its2.S )
Lrc<-rbind(Lrc.L , Lrc.Z, Lrc.R,Lrc.S )

#
da<-Lrc
da1<-da[da$RC<=-0.95,]
y  <- NULL;
t1<-levels(env.L$bb)
for (i in t1){
  tmp0<-nrow(da[da1$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y<-rbind(y, tmp1)
}
da2<-da[da$RC>-0.95 & da$RC<0.95,]
z  <- NULL;
for (i in t1){
  tmp0<-nrow(da2[da2$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  z<-rbind(z, tmp1)
}
da3<-da[da$RC>0.95,]
x  <- NULL;
for (i in t1){
  tmp0<-nrow(da3[da3$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  x<-rbind(x, tmp1)
}
xyz<-data.frame(y,z,x)
xyz$RC95pct<-z$tmp/(x$tmp+y$tmp+z$tmp)
LaggRC<-data.frame(xyz$i,xyz$RC95pct)
names(LaggRC)<-c("TP.TREAT", "RC95pct")
# bNTI.its2
da<-LbNTI.its2
da1<-da[da$bNTI.its2<=-2,]
y  <- NULL;
for (i in t1){
  tmp0<-nrow(da[da1$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y<-rbind(y, tmp1)
}
da2<-da[da$bNTI.its2>-2 & da$bNTI.its2<2,]
z  <- NULL;
for (i in t1){
  tmp0<-nrow(da2[da2$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  z<-rbind(z, tmp1)
}
da3<-da[da$bNTI.its2>2,]
x  <- NULL;
for (i in t1){
  tmp0<-nrow(da3[da3$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  x<-rbind(x, tmp1)
}
xyz<-data.frame(y,z,x)
xyz$bNTI.its22pct<-z$tmp/(x$tmp+y$tmp+z$tmp)
Lagg2bNTI.its2<-data.frame(xyz$i,xyz$bNTI.its22pct)
names(Lagg2bNTI.its2)<-c("TP.TREAT", "bNTI.its22pct")


#Lagg2bNTI.its2

#LbNTI.its2$TP.TREAT==Lrc$TP.TREAT
Lrc.bNTI.its2<-data.frame(Lrc, LbNTI.its2)
#Lrc.bNTI.its2$TP.TREAT==Lrc.bNTI.its2$TP.TREAT.1

Lrc.bNTI.its2<-data.frame(Lrc.bNTI.its2,1)


da<-Lrc.bNTI.its2
da1<-da[da$bNTI.its2>-2 & da$bNTI.its2<2 & da$RC> -0.95 & da$RC < 0.95 ,]
y  <- NULL;
for (i in t1){
  tmp0<-nrow(da[da1$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y<-rbind(y, tmp1)
}

da2<-da[-(da$bNTI.its2>-2 & da$bNTI.its2<2 & da$RC> -0.95 & da$RC < 0.95),]
z  <- NULL;
for (i in t1){
  tmp0<-nrow(da2[da2$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  z<-rbind(z, tmp1)
}

xyz<-data.frame(y,z)
xyz$bNTI.its22RC95pct<-y$tmp/(y$tmp+z$tmp)
Lagg2bNTI.its22RC95pct<-data.frame(xyz$i,xyz$bNTI.its22RC95pct)
names(Lagg2bNTI.its22RC95pct)<-c("TP.TREAT", "bNTI.its22RC95pct")

#aggregate(Lrc.bNTI.its2$X1, by=list(Occurence=Lrc.bNTI.its2$TP.TREAT), FUN=sum)

da<-Lrc.bNTI.its2

da1<-da[da$RC<= -0.95,]
y1  <- NULL;
for (i in t1){
  tmp0<-nrow(da1[da1$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y1<-rbind(y1, tmp1)
}
y1<-data.frame(y1, "RC <= -0.95")
names(y1)<-c("Value", "TP.TREAT", "RC.partition")

da2<-da[abs(da$RC)< 0.95,]
y2  <- NULL;
for (i in t1){
  tmp0<-nrow(da2[da2$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y2<-rbind(y2, tmp1)
}
y2<-data.frame(y2, "abs(RC) < 0.95")
names(y2)<-c("Value", "TP.TREAT", "RC.partition")


da3<-da[da$RC>=0.95,]
y3  <- NULL;
for (i in t1){
  tmp0<-nrow(da3[da3$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y3<-rbind(y3, tmp1)
}
y3<-data.frame(y3, "RC >= 0.95")
names(y3)<-c("Value", "TP.TREAT", "RC.partition")

RC.part<-rbind(y1,y2,y3)

#RC.part$TP.TREAT
RC.part2<-cSplit(RC.part, "TP.TREAT", ".")
RC.part2$TP.TREAT_1<-as.numeric(gsub("TP", "" , RC.part2$TP.TREAT_1))
RC.part.TP.TREAT<-RC.part2
names(RC.part.TP.TREAT)<-c("Value","RC.partition",  "TP", "Habitat", "Treatment")


###

da<-Lrc.bNTI.its2

da1<-da[da$bNTI.its2<= -2,]
y1  <- NULL;
for (i in t1){
  tmp0<-nrow(da1[da1$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y1<-rbind(y1, tmp1)
}
y1<-data.frame(y1, "bNTI.its2 <= -2")
names(y1)<-c("Value", "TP.TREAT", "bNTI.its2.partition")

da2<-da[abs(da$bNTI.its2)< 2,]
y2  <- NULL;
for (i in t1){
  tmp0<-nrow(da2[da2$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y2<-rbind(y2, tmp1)
}
y2<-data.frame(y2, "abs(bNTI.its2) < 2")
names(y2)<-c("Value", "TP.TREAT", "bNTI.its2.partition")


da3<-da[da$bNTI.its2>=2,]
y3  <- NULL;
for (i in t1){
  tmp0<-nrow(da3[da3$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y3<-rbind(y3, tmp1)
}
y3<-data.frame(y3, "bNTI.its2 >= 2")
names(y3)<-c("Value", "TP.TREAT", "bNTI.its2.partition")

bNTI.its2.part<-rbind(y1,y2,y3)

#bNTI.its2.part$TP.TREAT
bNTI.its2.part2<-cSplit(bNTI.its2.part, "TP.TREAT", ".")
bNTI.its2.part2$TP.TREAT_1<-as.numeric(gsub("TP", "" , bNTI.its2.part2$TP.TREAT_1))
bNTI.its2.part.TP.TREAT<-bNTI.its2.part2
names(bNTI.its2.part.TP.TREAT)<-c("Value","bNTI.its2.partition",  "TP", "Habitat", "Treatment")
#
da<-Lrc.bNTI.its2

da1<-da[abs(da$bNTI.its2)<2 & da$RC<= -0.95,]
y1  <- NULL;
for (i in t1){
  tmp0<-nrow(da1[da1$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y1<-rbind(y1, tmp1)
}
y1<-data.frame(y1, "abs(bNTI.its2) < 2 & RC <= -0.95")
names(y1)<-c("Value", "TP.TREAT", "bNTI.its2.RC.partition")

da2<-da[abs(da$bNTI.its2)< 2 & abs(da$RC)< 0.95,]
y2  <- NULL;
for (i in t1){
  tmp0<-nrow(da2[da2$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y2<-rbind(y2, tmp1)
}
y2<-data.frame(y2, "abs(bNTI.its2) < 2 & abs(RC) < 0.95")
names(y2)<-c("Value", "TP.TREAT", "bNTI.its2.RC.partition")


da3<-da[abs(da$bNTI.its2)<2 & da$RC>=0.95,]
y3  <- NULL;
for (i in t1){
  tmp0<-nrow(da3[da3$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y3<-rbind(y3, tmp1)
}
y3<-data.frame(y3, "abs(bNTI.its2) < 2 & RC >= 0.95")
names(y3)<-c("Value", "TP.TREAT", "bNTI.its2.RC.partition")

da4<-da[da$bNTI.its2>=2 & da$RC>=0.95,]
y4  <- NULL;
for (i in t1){
  tmp0<-nrow(da4[da4$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y4<-rbind(y4, tmp1)
}

y4<-data.frame(y4, "bNTI.its2 >= 2 & RC >= 0.95")
names(y4)<-c("Value", "TP.TREAT", "bNTI.its2.RC.partition")


da5<-da[da$bNTI.its2>=2 & abs(da$RC)< 0.95,]
y5  <- NULL;
for (i in t1){
  tmp0<-nrow(da5[da5$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y5<-rbind(y5, tmp1)
}

y5<-data.frame(y5, "bNTI.its2 >= 2 & abs(RC) < 0.95")
names(y5)<-c("Value", "TP.TREAT", "bNTI.its2.RC.partition")


da6<-da[da$bNTI.its2>=2 & da$RC<= -0.95,]
y6  <- NULL;
for (i in t1){
  tmp0<-nrow(da6[da6$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y6<-rbind(y6, tmp1)
}

y6<-data.frame(y6, "bNTI.its2 >= 2 & RC <= -0.95")
names(y6)<-c("Value", "TP.TREAT", "bNTI.its2.RC.partition")


#
da7<-da[da$bNTI.its2<= -2 & da$RC>=0.95,]
y7  <- NULL;
for (i in t1){
  tmp0<-nrow(da7[da7$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y7<-rbind(y7, tmp1)
}

y7<-data.frame(y7, "bNTI.its2 <= -2 & RC >= 0.95")
names(y7)<-c("Value", "TP.TREAT", "bNTI.its2.RC.partition")


da8<-da[da$bNTI.its2<= -2 & abs(da$RC)< 0.95,]
y8  <- NULL;
for (i in t1){
  tmp0<-nrow(da8[da8$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y8<-rbind(y8, tmp1)
}

y8<-data.frame(y8, "bNTI.its2 <= -2 & abs(RC) < 0.95")
names(y8)<-c("Value", "TP.TREAT", "bNTI.its2.RC.partition")


da9<-da[da$bNTI.its2<= -2 & da$RC<= -0.95,]
y9  <- NULL;
for (i in t1){
  tmp0<-nrow(da9[da9$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y9<-rbind(y9, tmp1)
}

y9<-data.frame(y9, "bNTI.its2 <= -2 & RC < -0.95")
names(y9)<-c("Value", "TP.TREAT", "bNTI.its2.RC.partition")


#y6 <-15 - (y1$Value+y2$Value+y3$Value+y4$Value+y5$Value+y6$Value+y7$Value+y8$Value+y9$Value)
#y6<-data.frame(y6,y1$TP.TREAT, "Others")
#names(y6)<-c("Value", "TP.TREAT", "bNTI.its2.RC.partition")
bNTI.its2.RC.part<-rbind(y1,y2,y3,y4,y5, y6, y7, y8,y9)

#bNTI.its2.RC.part$TP.TREAT
bNTI.its2.RC.part2<-cSplit(bNTI.its2.RC.part, "TP.TREAT", ".")
bNTI.its2.RC.part2$TP.TREAT_1<-as.numeric(gsub("TP", "" , bNTI.its2.RC.part2$TP.TREAT_1))
bNTI.its2.RC.part.TP.TREAT<-bNTI.its2.RC.part2
names(bNTI.its2.RC.part.TP.TREAT)<-c("Value","bNTI.its2.RC.partition",  "TP", "Habitat", "Treatment")


#SCNM

source("sncm.fit.R")
#tmp<-read.csv("fungL.R362F.csv", head =T, row.names =1)
d.ck<-data.frame()
for (j in c("Root", "Rhizosphere", "Leaf", "Soil")){
  for (i in c(1:17)){
    tmp0<-tmp[env.L$Treatment1=="Control" & env.L$Habitat== j & env.L$TP== i,]
    dd<-data.frame(sncm.fit(tmp0),j,i, "Control")
    d.ck<-rbind(d.ck, dd)
  }
}


tmp0<-tmp[env.L$Treatment1=="Control" & env.L$Habitat== "Soil" & env.L$TP== 0,]
dd<-data.frame(sncm.fit(tmp0),"Soil", 0 , "Control")
names(dd)<-names(d.ck)
d.ck<-rbind(d.ck, dd)

tmp0<-tmp[env.L$Treatment1=="Pre_flowering_drought" & env.L$Habitat== "Soil" & env.L$TP== 0,]
dd<-data.frame(sncm.fit(tmp0),"Soil", 0 , "Pre_flowering_drought")
names(dd)<-names(d.ck)
d.ck<-rbind(d.ck, dd)

tmp0<-tmp[env.L$Treatment1=="Post_flowering_drought" & env.L$Habitat== "Soil" & env.L$TP== 0,]
dd<-data.frame(sncm.fit(tmp0),"Soil", 0 , "Post_flowering_drought")
names(dd)<-names(d.ck)
d.ck<-rbind(d.ck, dd)

d.pr<-data.frame()
for (j in c("Root", "Rhizosphere", "Leaf", "Soil")){
  for (i in c(3:17)){
    tmp0<-tmp[env.L$Treatment1=="Pre_flowering_drought" & env.L$Habitat== j & env.L$TP== i,]
    dd<-data.frame(sncm.fit(tmp0),j,i, "Pre_flowering_drought")
    d.pr<-rbind(d.pr, dd)
  }
}

d.po<-data.frame()
for (j in c("Root", "Rhizosphere", "Leaf", "Soil")){
  for (i in c(8:17)){
    tmp0<-tmp[env.L$Treatment1=="Post_flowering_drought"& env.L$Habitat== j & env.L$TP== i,]
    dd<-data.frame(sncm.fit(tmp0),j,i, "Post_flowering_drought")
    d.po<-rbind(d.po, dd)
  }
}
names(d.po)<-names(d.pr)<-names(d.ck)
L.sncm<-rbind(d.po,d.pr,d.ck)
#L.sncm$X.Control.
L.sncm$lev<-interaction(L.sncm$j,L.sncm$X.Control.,L.sncm$i,sep = ":")
names(L.sncm)<-c( "m","m.ci","m.mle","maxLL","binoLL","poisLL","Rsqr","Rsqr.bino","Rsqr.pois","RMSE","RMSE.bino","RMSE.pois","AIC","BIC","AIC.bino","BIC.bino","AIC.pois","BIC.pois","N","Samples","Richness","Detect","Habitat", "TP", "Treatment","Level")

t1<-levels(droplevels(env.L$bb))
Fst = NULL
for (i in t1){
  m1<-w.fst(tmp[env.L$bb== i,])
  m1<-data.frame(m1, i)
  Fst<-rbind(Fst,m1)
}
names(Fst)<-c("Fst", "TP.TREAT")

phylo = read.tree("EPICON.fungi.tree.txt");
#phylo; # a summary of the phylogeny
#plot.phylo(phylo,typ="fan", font =1, cex=1)
bNTI.its2<-read.csv("weighted_bNTI.its2.F.csv", head = T, row.names =1)
bNTI.its2<-as.dist(bNTI.its2)
bNTI.its201<-(bNTI.its2-min(bNTI.its2))/(max(bNTI.its2)-min(bNTI.its2))

#RC
rc0<-read.csv("rc.RSZL.F.csv", head = T, row.names =1)
rc<-as.dist(rc0)
rc01<-(rc+1)/2

env.L$va<-interaction(env.L$TP, env.L$Habitat2)
fd<-beta.pair(tmp01, index.family = "jaccard")
bc<-vegdist(tmp)
bd.rc<-betadisper(rc01,env.L$va)
env.L$RCdisper<-bd.rc$distances
bd.bc<-betadisper(bc,env.L$va)
env.L$bradisper<-bd.bc$distances
bd.jac<-betadisper(fd$beta.jac,env.L$va)
env.L$jacdisper<-bd.jac$distances
bd.jne<-betadisper(fd$beta.jne,env.L$va)
env.L$jnedisper<-bd.jne$distances
bd.jtu<-betadisper(fd$beta.jtu,env.L$va)
env.L$jtudisper<-bd.jtu$distances
bd.bNTI.its201<-betadisper(bNTI.its201,env.L$va)
env.L$bNTI.its2disper<-bd.bNTI.its201$distances

##Meta data###
#env.L$Fungi.pct<-rowSums(fungL.rawF)/colSums(fung0.L[,26:277])
env.L$S.raw<-specnumber(fung.raw)
env.L$S.rar362<-specnumber(tmp)
env.L$OTU15_Ustilago<-tmp$OTU15_Ustilago
env.L$yeasts<-tmp$OTU26_Sporobolomyces+tmp$OTU10_Filobasidium+tmp$OTU24_Cryptococcus+tmp$OTU14_Symmetrospora
Laggmeta<-aggregate(cbind(env.L$Fungi.pct, env.L$S.raw, env.L$S.rar362,env.L$RCdisper, 
                          env.L$bradisper, env.L$jacdisper, env.L$jnedisper, 
                          env.L$jtudisper),by=list(env.L$bb) , mean)
names(Laggmeta)<-c("TP.TREAT","Fungi.pct", "S.raw", "S.rar362", "RCdisper", "bradisper",
                   "jacdisper", "jnedisper", "jtudisper")
Lagg<-merge(LaggRC,  Laggmeta, by="TP.TREAT", all = FALSE)
Lagg<-merge(Lagg,  Lagg2bNTI.its2,  by="TP.TREAT", all = FALSE)
Lagg<-merge(Lagg,  Lagg2bNTI.its22RC95pct, by="TP.TREAT", all = FALSE)

fung.L1<-cSplit(Lagg, "TP.TREAT", ".")
fung.L1$TP.TREAT_1<-as.numeric(gsub("TP", "" , fung.L1$TP.TREAT_1))
fung.L1$Level<-interaction(fung.L1$TP.TREAT_2,fung.L1$TP.TREAT_3 ,fung.L1$TP.TREAT_1 ,sep = ":")
Lagg<-data.frame(fung.L1$Level,Lagg)
Lagg<-merge(Lagg, L.sncm, by.x="fung.L1.Level", by.y= "Level", all= TRUE )
#L.sncm$Level
#Lagg$fung.L1.Level
Lagg<-merge(Lagg,Fst, by="TP.TREAT")

## LaggqPCR
env.LqPCR<-env.L[env.L$qPCR > 0, ]
LaggqPCRmeta<-aggregate(cbind(env.LqPCR$Fungi.pct,env.LqPCR$qPCR, env.LqPCR$S.raw, env.LqPCR$S.rar362,
                              env.LqPCR$RCdisper, env.LqPCR$bradisper, env.LqPCR$jacdisper, 
                              env.LqPCR$jnedisper,env.LqPCR$jtudisper),by=list(env.LqPCR$bb) , mean)

names(LaggqPCRmeta)<-c("TP.TREAT","Fungi.pct", "qPCR", "S.raw", "S.rar362", "RCdisper", "bradisper",
                       "jacdisper", "jnedisper", "jtudisper")


LaggqPCR<-merge(LaggRC,  LaggqPCRmeta, by="TP.TREAT", all = FALSE)
LaggqPCR<-merge(LaggqPCR,  Lagg2bNTI.its2,  by="TP.TREAT", all = FALSE)
LaggqPCR<-merge(LaggqPCR,  Lagg2bNTI.its22RC95pct, by="TP.TREAT", all = FALSE)


fung.L1qPCR<-cSplit(LaggqPCR, "TP.TREAT", ".")
fung.L1qPCR$TP.TREAT_1<-as.numeric(gsub("TP", "" , fung.L1qPCR$TP.TREAT_1))
fung.L1qPCR$Level<-interaction(fung.L1qPCR$TP.TREAT_2,fung.L1qPCR$TP.TREAT_3 ,fung.L1qPCR$TP.TREAT_1 ,sep = ":")
LaggqPCR<-data.frame(fung.L1qPCR$Level,LaggqPCR)
LaggqPCR<-merge(LaggqPCR, L.sncm, by.x="fung.L1qPCR.Level", by.y= "Level", all= TRUE )

LaggqPCR<-merge(LaggqPCR,Fst, by="TP.TREAT")

##Meta data Transcriptome###

LaggmetaMet<-aggregate(cbind(env.Tra$Pct.Tra, 
                             env.Tra$S.rar362,env.Tra$RCdisper, env.Tra$bradisper,
                             env.Tra$jacdisper, env.Tra$jnedisper, 
                             env.Tra$jtudisper),by=list(env.Tra$bb) , mean)
names(LaggmetaMet)<-c("TP.TREAT","Fungi.pct.tra", "S.rar362", "RCdisper", "bradisper",
                      "jacdisper", "jnedisper", "jtudisper")
Traagg<-merge(LaggRC, LaggmetaMet, by="TP.TREAT", all = FALSE)
Traagg<-merge(Traagg,  Lagg2bNTI.its2, by="TP.TREAT", all = FALSE)
Traagg<-merge(Traagg,  Lagg2bNTI.its22RC95pct, by="TP.TREAT", all = FALSE)
fung.L1<-cSplit(Traagg, "TP.TREAT", ".")
fung.L1$TP.TREAT_1<-as.numeric(gsub("TP", "" , fung.L1$TP.TREAT_1))
#fung.L1$Level<-interaction(fung.L1$TP.TREAT_2,fung.L1$TP.TREAT_1 ,sep = ":")
fung.L1$Level<-interaction(fung.L1$TP.TREAT_2,fung.L1$TP.TREAT_3 ,fung.L1$TP.TREAT_1 ,sep = ":")
Traagg<-data.frame(fung.L1$Level,Traagg)
Traagg<-merge(Traagg, L.sncm, by.x="fung.L1.Level", by.y= "Level", all= FALSE )
Traagg<-merge(Traagg,Fst, by="TP.TREAT")



save.image("EPICON.data.preparation.RC.bNTI.its2.2019.03.17.Rdata")

rm(list = ls())

######DATA PREPARATION RC BNTI GHOSTTREE#####

rm(list = ls())


setwd("/Users/chengg/Google Drive/EPICON/Mycobiome/Fungal ITS/statistic/Total.fungi")
library(reshape2)
library(ggplot2)
library(MASS)
library(splitstackshape)
library(colorRamps)
library(vegan)
library(betapart)
library(ape)
library(DOC)
library(ecodist)
library(gridExtra)
library(nlme)
library(MuMIn)
source("weighted Fst function.r")
env0<-read.csv("epicon.ENV.2017.12.05.csv", head = T)
fung0<-read.csv("epicon.ID.mat.2018.06.12.csv", head=T, row.names =1) ##Read in the raw data###

gr<-fung0$Fungi=="Fungi"
#gr<-fung0$Phylum=="Basidiomycota"

fungt<-data.frame(fung0[gr ,c(1:1251) ]) ### raw data of all samples including pseudo samples #
ID<-data.frame(fung0[gr ,c(-1:-1251) ]) ### raw data of all samples including pseudo samples #
ID1<-data.frame(rownames(ID),ID$Phylum_lifestyle, ID$Phylum)
#names(ID1)<- c("ID", "Phylum_lifestyle", "Phylum", "Life_style")
#Flev<-ID$Phylum
#Flev<-ID$Phylum_lifestyle
Flev<-rownames(ID);
taxonomy<-data.frame(ID$Kingdom,ID$Phylum.ab, ID$Class.ab, ID$Order, ID$Family, ID$Genus);
colnames(taxonomy) = c("kingdom","phylum","class","order","family","genus");
rownames(taxonomy)<-rownames(ID)
fung.lev<-data.frame(aggregate(fungt,by=list(Flev) , sum))
rownames(fung.lev)<-fung.lev[,1]; fung.lev<-fung.lev[match(Flev, fung.lev$Group.1),]
fung.lev<-fung.lev[,-1]
fung1<-data.frame(t(fung.lev))

fung.raw.pseudo<-fung1[env0$Habitat!="Prop_root",]  # can be useful for Barplots of total fungi
env.F.raw.pseudo<-env0[env0$Habitat!="Prop_root",]   # can be useful for Barplots of total fungi

fung.raw<-fung.raw.pseudo[c(1:1026),] ### raw data of all samples #
env.raw<-env.F.raw.pseudo[c(1:1026),]

cutoff<-362 # the cutoff for rarefaction

fung.rar<-data.frame(rrarefy(fung.raw, cutoff))   
env<-env.raw[rowSums(fung.rar)==cutoff,]
fung<-fung.rar[rowSums(fung.rar)==cutoff,colSums(fung.rar)>0]
fung<-fung[,colSums(fung)>0]

# bNTI.ghost
#phylo = read.tree("EPICON.fungi.tree.txt");
#phylo; # a summary of the phylogeny
#plot.phylo(phylo,typ="fan", font =1, cex=1)
bNTI.ghost<-read.csv("weighted_bNTI.ghost.F.csv", head = T, row.names =1)
bNTI.ghost<-as.dist(bNTI.ghost)
bNTI.ghost01<-(bNTI.ghost-min(bNTI.ghost))/(max(bNTI.ghost)-min(bNTI.ghost))

#RC
rc0<-read.csv("rc.RSZL.F.csv", head = T, row.names =1)
rc<-as.dist(rc0)
rc01<-(rc+1)/2

env.L<-env
fungL.R362F<-fung
tmp<-fung ## abudance data

tmp01<-tmp
tmp01[tmp01>0]=1      # 0 1 data
env.L$S.rar362<-specnumber(fungL.R362F)
env.L$H.rar362<-vegan::diversity(fungL.R362F)
env.L$J.rar362<-env.L$H.rar362/log(env.L$S.rar362)
env.L$TP1[env.L$TP>7]="Weeks8_17" ; env.L$TP1[env.L$TP<8]="Weeks1_7" # to divide all time points to early and later groups
env.L$bb<-droplevels(interaction( env.L$Timepiont,env.L$Habitat,env.L$Treatment1,sep = "."))
env.L$Habitat2<-factor(droplevels(env.L$Habitat), levels=c("Leaf", "Root", "Rhizosphere", "Soil"),
                       labels = c("L", "R", "Z", "S"))
env.L$aa1<-paste("TP",env.L$TP, env.L$Habitat2,env.L$plot, sep = "")

env.L$va<-interaction(env.L$TP, env.L$Habitat2)

phylo = read.tree("EPICON.fungi.tree.txt");
#phylo; # a summary of the phylogeny
#plot.phylo(phylo,typ="fan", font =1, cex=1)
bNTI.ghost<-read.csv("weighted_bNTI.ghost.F.csv", head = T, row.names =1)
bNTI.ghost<-as.dist(bNTI.ghost)
bNTI.ghost01<-(bNTI.ghost-min(bNTI.ghost))/(max(bNTI.ghost)-min(bNTI.ghost))

#RC
rc0<-read.csv("rc.RSZL.F.csv", head = T, row.names =1)
rc<-as.dist(rc0)
rc01<-(rc+1)/2

env.L$va<-interaction(env.L$TP, env.L$Habitat2)
fd<-beta.pair(tmp01, index.family = "jaccard")
bc<-vegdist(tmp)
bd.rc<-betadisper(rc01,env.L$va)
env.L$RCdisper<-bd.rc$distances
bd.bc<-betadisper(bc,env.L$va)
env.L$bradisper<-bd.bc$distances
bd.jac<-betadisper(fd$beta.jac,env.L$va)
env.L$jacdisper<-bd.jac$distances
bd.jne<-betadisper(fd$beta.jne,env.L$va)
env.L$jnedisper<-bd.jne$distances
bd.jtu<-betadisper(fd$beta.jtu,env.L$va)
env.L$jtudisper<-bd.jtu$distances
bd.bNTI.ghost01<-betadisper(bNTI.ghost01,env.L$va)
env.L$bNTI.ghostdisper<-bd.bNTI.ghost01$distances

###################################### 
# Transcriptome samples level metrics#
######################################

Tra<-read.csv("LR.mycotranscriptome.csv", head = T)

env.Tra<- merge(Tra,env.L, by.x="aa", by.y="aa1", all =FALSE)
env.Tra$Pct.Tra<-rowSums(env.Tra[,c(12:20,22:24)])/env.Tra$FilteredReads
tmp.Tra<-tmp[rownames(tmp) %in% env.Tra$aa,]
tmp.Tra<-tmp.Tra[colSums(tmp.Tra)>0] ## abudance data
tmp.Tra01<-tmp.Tra
tmp.Tra01[tmp.Tra01>0]=1 

###################################### 
# Metabolome samples level metrics#
######################################

Met<-read.csv("EPICON.metabolome.csv", head = T)
env.Tra.Met<-env.Tra[env.Tra$aa %in% Met$aa,]
Met1<-Met[Met$aa %in% env.Tra.Met$aa,]
tmp.Tra.Met<-tmp.Tra[rownames(tmp.Tra) %in% env.Tra.Met$aa,]## abudance data
tmp.Tra.Met01<-tmp.Tra.Met
tmp.Tra.Met01[tmp.Tra.Met01>0]=1 

##############################################
## To aggarete variables by TP.TREAT##
##############################################

bNTI.ghost<-read.csv("weighted_bNTI.ghost.S.F.csv", head = T, row.names =1)
bNTI.ghost<-as.dist(bNTI.ghost)
bNTI.ghost.01<-(bNTI.ghost-min(bNTI.ghost))/(max(bNTI.ghost)-min(bNTI.ghost))

rc0<-read.csv("rc.S.F.csv", head = T, row.names =1)
rc<-as.dist(rc0)
rc.01<-(rc+1)/2

env.L1<-droplevels(env.L[env.L$Habitat=="Soil",])

t1<-levels(env.L1$bb)
LbNTI.ghost = NULL
for (i in t1){
  m1<-as.matrix(bNTI.ghost)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  LbNTI.ghost<-rbind(LbNTI.ghost,m1)
}
LbNTI.ghost2<-cSplit(LbNTI.ghost, "TP.TREAT", ".")
LbNTI.ghost2$TP.TREAT_1<-as.numeric(gsub("TP", "" , LbNTI.ghost2$TP.TREAT_1))
LbNTI.ghost.TP.TREAT<-LbNTI.ghost2
names(LbNTI.ghost.TP.TREAT)<-c("bNTI.ghost", "TP","Habitat", "Treatment")
LbNTI.ghost<-data.frame(LbNTI.ghost$TP.TREAT,LbNTI.ghost.TP.TREAT)
names(LbNTI.ghost)<-c("TP.TREAT", "bNTI.ghost", "TP","Habitat", "Treatment")
# RC
t1<-levels(env.L1$bb)
Lrc = NULL
for (i in t1){
  m1<-as.matrix(rc)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  Lrc<-rbind(Lrc,m1)
}
Lrc2<-cSplit(Lrc, "TP.TREAT", ".")
Lrc2$TP.TREAT_1<-as.numeric(gsub("TP", "" , Lrc2$TP.TREAT_1))
RC.TP.TREAT<-Lrc2
names(RC.TP.TREAT)<-c("RC", "TP","Habitat", "Treatment")
Lrc<-data.frame(Lrc$TP.TREAT,Lrc2)
names(Lrc)<-c("TP.TREAT", "RC", "TP","Habitat", "Treatment")
LbNTI.ghost.S<-LbNTI.ghost
Lrc.S<-Lrc

#
bNTI.ghost<-read.csv("weighted_bNTI.ghost.Z.F.csv", head = T, row.names =1)
bNTI.ghost<-as.dist(bNTI.ghost)
bNTI.ghost.01<-(bNTI.ghost-min(bNTI.ghost))/(max(bNTI.ghost)-min(bNTI.ghost))

rc0<-read.csv("rc.Z.F.csv", head = T, row.names =1)
rc<-as.dist(rc0)
rc.01<-(rc+1)/2

env.L1<-droplevels(env.L[env.L$Habitat=="Rhizosphere",])

t1<-levels(env.L1$bb)
LbNTI.ghost = NULL
for (i in t1){
  m1<-as.matrix(bNTI.ghost)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  LbNTI.ghost<-rbind(LbNTI.ghost,m1)
}
LbNTI.ghost2<-cSplit(LbNTI.ghost, "TP.TREAT", ".")
LbNTI.ghost2$TP.TREAT_1<-as.numeric(gsub("TP", "" , LbNTI.ghost2$TP.TREAT_1))
LbNTI.ghost.TP.TREAT<-LbNTI.ghost2
names(LbNTI.ghost.TP.TREAT)<-c("bNTI.ghost", "TP","Habitat", "Treatment")
LbNTI.ghost<-data.frame(LbNTI.ghost$TP.TREAT,LbNTI.ghost.TP.TREAT)
names(LbNTI.ghost)<-c("TP.TREAT", "bNTI.ghost", "TP","Habitat", "Treatment")
# RC
t1<-levels(env.L1$bb)
Lrc = NULL
for (i in t1){
  m1<-as.matrix(rc)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  Lrc<-rbind(Lrc,m1)
}
Lrc2<-cSplit(Lrc, "TP.TREAT", ".")
Lrc2$TP.TREAT_1<-as.numeric(gsub("TP", "" , Lrc2$TP.TREAT_1))
RC.TP.TREAT<-Lrc2
names(RC.TP.TREAT)<-c("RC", "TP","Habitat", "Treatment")
Lrc<-data.frame(Lrc$TP.TREAT,Lrc2)
names(Lrc)<-c("TP.TREAT", "RC", "TP","Habitat", "Treatment")
LbNTI.ghost.Z<-LbNTI.ghost
Lrc.Z<-Lrc

#
bNTI.ghost<-read.csv("weighted_bNTI.ghost.R.F.csv", head = T, row.names =1)
bNTI.ghost<-as.dist(bNTI.ghost)
bNTI.ghost.01<-(bNTI.ghost-min(bNTI.ghost))/(max(bNTI.ghost)-min(bNTI.ghost))

rc0<-read.csv("rc.R.F.csv", head = T, row.names =1)
rc<-as.dist(rc0)
rc.01<-(rc+1)/2

env.L1<-droplevels(env.L[env.L$Habitat=="Root",])

t1<-levels(env.L1$bb)
LbNTI.ghost = NULL
for (i in t1){
  m1<-as.matrix(bNTI.ghost)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  LbNTI.ghost<-rbind(LbNTI.ghost,m1)
}
LbNTI.ghost2<-cSplit(LbNTI.ghost, "TP.TREAT", ".")
LbNTI.ghost2$TP.TREAT_1<-as.numeric(gsub("TP", "" , LbNTI.ghost2$TP.TREAT_1))
LbNTI.ghost.TP.TREAT<-LbNTI.ghost2
names(LbNTI.ghost.TP.TREAT)<-c("bNTI.ghost", "TP","Habitat", "Treatment")
LbNTI.ghost<-data.frame(LbNTI.ghost$TP.TREAT,LbNTI.ghost.TP.TREAT)
names(LbNTI.ghost)<-c("TP.TREAT", "bNTI.ghost", "TP","Habitat", "Treatment")
# RC
t1<-levels(env.L1$bb)
Lrc = NULL
for (i in t1){
  m1<-as.matrix(rc)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  Lrc<-rbind(Lrc,m1)
}
Lrc2<-cSplit(Lrc, "TP.TREAT", ".")
Lrc2$TP.TREAT_1<-as.numeric(gsub("TP", "" , Lrc2$TP.TREAT_1))
RC.TP.TREAT<-Lrc2
names(RC.TP.TREAT)<-c("RC", "TP","Habitat", "Treatment")
Lrc<-data.frame(Lrc$TP.TREAT,Lrc2)
names(Lrc)<-c("TP.TREAT", "RC", "TP","Habitat", "Treatment")
LbNTI.ghost.R<-LbNTI.ghost
Lrc.R<-Lrc

#
bNTI.ghost<-read.csv("weighted_bNTI.ghost.L.F.csv", head = T, row.names =1)
bNTI.ghost<-as.dist(bNTI.ghost)
bNTI.ghost.01<-(bNTI.ghost-min(bNTI.ghost))/(max(bNTI.ghost)-min(bNTI.ghost))

rc0<-read.csv("rc.L.F.csv", head = T, row.names =1)
rc<-as.dist(rc0)
rc.01<-(rc+1)/2

env.L1<-droplevels(env.L[env.L$Habitat=="Leaf",])

t1<-levels(env.L1$bb)
LbNTI.ghost = NULL
for (i in t1){
  m1<-as.matrix(bNTI.ghost)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  LbNTI.ghost<-rbind(LbNTI.ghost,m1)
}
LbNTI.ghost2<-cSplit(LbNTI.ghost, "TP.TREAT", ".")
LbNTI.ghost2$TP.TREAT_1<-as.numeric(gsub("TP", "" , LbNTI.ghost2$TP.TREAT_1))
LbNTI.ghost.TP.TREAT<-LbNTI.ghost2
names(LbNTI.ghost.TP.TREAT)<-c("bNTI.ghost", "TP","Habitat", "Treatment")
LbNTI.ghost<-data.frame(LbNTI.ghost$TP.TREAT,LbNTI.ghost.TP.TREAT)
names(LbNTI.ghost)<-c("TP.TREAT", "bNTI.ghost", "TP","Habitat", "Treatment")
# RC
t1<-levels(env.L1$bb)
Lrc = NULL
for (i in t1){
  m1<-as.matrix(rc)[grep(i, env.L1$bb), grep(i, env.L1$bb) ]
  m1<-data.frame(melt(m1[lower.tri(m1, diag = FALSE)]))
  m1$TP.TREAT=i
  #m1$Habitat="Leaf"
  Lrc<-rbind(Lrc,m1)
}
Lrc2<-cSplit(Lrc, "TP.TREAT", ".")
Lrc2$TP.TREAT_1<-as.numeric(gsub("TP", "" , Lrc2$TP.TREAT_1))
RC.TP.TREAT<-Lrc2
names(RC.TP.TREAT)<-c("RC", "TP","Habitat", "Treatment")
Lrc<-data.frame(Lrc$TP.TREAT,Lrc2)
names(Lrc)<-c("TP.TREAT", "RC", "TP","Habitat", "Treatment")

LbNTI.ghost.L<-LbNTI.ghost
Lrc.L<-Lrc

LbNTI.ghost<-rbind(LbNTI.ghost.L , LbNTI.ghost.Z, LbNTI.ghost.R,LbNTI.ghost.S )
Lrc<-rbind(Lrc.L , Lrc.Z, Lrc.R,Lrc.S )

#
da<-Lrc
da1<-da[da$RC<=-0.95,]
y  <- NULL;
t1<-levels(env.L$bb)
for (i in t1){
  tmp0<-nrow(da[da1$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y<-rbind(y, tmp1)
}
da2<-da[da$RC>-0.95 & da$RC<0.95,]
z  <- NULL;
for (i in t1){
  tmp0<-nrow(da2[da2$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  z<-rbind(z, tmp1)
}
da3<-da[da$RC>0.95,]
x  <- NULL;
for (i in t1){
  tmp0<-nrow(da3[da3$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  x<-rbind(x, tmp1)
}
xyz<-data.frame(y,z,x)
xyz$RC95pct<-z$tmp/(x$tmp+y$tmp+z$tmp)
LaggRC<-data.frame(xyz$i,xyz$RC95pct)
names(LaggRC)<-c("TP.TREAT", "RC95pct")
# bNTI.ghost
da<-LbNTI.ghost
da1<-da[da$bNTI.ghost<=-2,]
y  <- NULL;
for (i in t1){
  tmp0<-nrow(da[da1$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y<-rbind(y, tmp1)
}
da2<-da[da$bNTI.ghost>-2 & da$bNTI.ghost<2,]
z  <- NULL;
for (i in t1){
  tmp0<-nrow(da2[da2$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  z<-rbind(z, tmp1)
}
da3<-da[da$bNTI.ghost>2,]
x  <- NULL;
for (i in t1){
  tmp0<-nrow(da3[da3$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  x<-rbind(x, tmp1)
}
xyz<-data.frame(y,z,x)
xyz$bNTI.ghost2pct<-z$tmp/(x$tmp+y$tmp+z$tmp)
Lagg2bNTI.ghost<-data.frame(xyz$i,xyz$bNTI.ghost2pct)
names(Lagg2bNTI.ghost)<-c("TP.TREAT", "bNTI.ghost2pct")


#Lagg2bNTI.ghost

#LbNTI.ghost$TP.TREAT==Lrc$TP.TREAT
Lrc.bNTI.ghost<-data.frame(Lrc, LbNTI.ghost)
#Lrc.bNTI.ghost$TP.TREAT==Lrc.bNTI.ghost$TP.TREAT.1

Lrc.bNTI.ghost<-data.frame(Lrc.bNTI.ghost,1)


da<-Lrc.bNTI.ghost
da1<-da[da$bNTI.ghost>-2 & da$bNTI.ghost<2 & da$RC> -0.95 & da$RC < 0.95 ,]
y  <- NULL;
for (i in t1){
  tmp0<-nrow(da[da1$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y<-rbind(y, tmp1)
}

da2<-da[-(da$bNTI.ghost>-2 & da$bNTI.ghost<2 & da$RC> -0.95 & da$RC < 0.95),]
z  <- NULL;
for (i in t1){
  tmp0<-nrow(da2[da2$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  z<-rbind(z, tmp1)
}

xyz<-data.frame(y,z)
xyz$bNTI.ghost2RC95pct<-y$tmp/(y$tmp+z$tmp)
Lagg2bNTI.ghost2RC95pct<-data.frame(xyz$i,xyz$bNTI.ghost2RC95pct)
names(Lagg2bNTI.ghost2RC95pct)<-c("TP.TREAT", "bNTI.ghost2RC95pct")

#aggregate(Lrc.bNTI.ghost$X1, by=list(Occurence=Lrc.bNTI.ghost$TP.TREAT), FUN=sum)

da<-Lrc.bNTI.ghost

da1<-da[da$RC<= -0.95,]
y1  <- NULL;
for (i in t1){
  tmp0<-nrow(da1[da1$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y1<-rbind(y1, tmp1)
}
y1<-data.frame(y1, "RC <= -0.95")
names(y1)<-c("Value", "TP.TREAT", "RC.partition")

da2<-da[abs(da$RC)< 0.95,]
y2  <- NULL;
for (i in t1){
  tmp0<-nrow(da2[da2$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y2<-rbind(y2, tmp1)
}
y2<-data.frame(y2, "abs(RC) < 0.95")
names(y2)<-c("Value", "TP.TREAT", "RC.partition")


da3<-da[da$RC>=0.95,]
y3  <- NULL;
for (i in t1){
  tmp0<-nrow(da3[da3$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y3<-rbind(y3, tmp1)
}
y3<-data.frame(y3, "RC >= 0.95")
names(y3)<-c("Value", "TP.TREAT", "RC.partition")

RC.part<-rbind(y1,y2,y3)

#RC.part$TP.TREAT
RC.part2<-cSplit(RC.part, "TP.TREAT", ".")
RC.part2$TP.TREAT_1<-as.numeric(gsub("TP", "" , RC.part2$TP.TREAT_1))
RC.part.TP.TREAT<-RC.part2
names(RC.part.TP.TREAT)<-c("Value","RC.partition",  "TP", "Habitat", "Treatment")


###

da<-Lrc.bNTI.ghost

da1<-da[da$bNTI.ghost<= -2,]
y1  <- NULL;
for (i in t1){
  tmp0<-nrow(da1[da1$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y1<-rbind(y1, tmp1)
}
y1<-data.frame(y1, "bNTI.ghost <= -2")
names(y1)<-c("Value", "TP.TREAT", "bNTI.ghost.partition")

da2<-da[abs(da$bNTI.ghost)< 2,]
y2  <- NULL;
for (i in t1){
  tmp0<-nrow(da2[da2$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y2<-rbind(y2, tmp1)
}
y2<-data.frame(y2, "abs(bNTI.ghost) < 2")
names(y2)<-c("Value", "TP.TREAT", "bNTI.ghost.partition")


da3<-da[da$bNTI.ghost>=2,]
y3  <- NULL;
for (i in t1){
  tmp0<-nrow(da3[da3$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y3<-rbind(y3, tmp1)
}
y3<-data.frame(y3, "bNTI.ghost >= 2")
names(y3)<-c("Value", "TP.TREAT", "bNTI.ghost.partition")

bNTI.ghost.part<-rbind(y1,y2,y3)

#bNTI.ghost.part$TP.TREAT
bNTI.ghost.part2<-cSplit(bNTI.ghost.part, "TP.TREAT", ".")
bNTI.ghost.part2$TP.TREAT_1<-as.numeric(gsub("TP", "" , bNTI.ghost.part2$TP.TREAT_1))
bNTI.ghost.part.TP.TREAT<-bNTI.ghost.part2
names(bNTI.ghost.part.TP.TREAT)<-c("Value","bNTI.ghost.partition",  "TP", "Habitat", "Treatment")
#
da<-Lrc.bNTI.ghost

da1<-da[abs(da$bNTI.ghost)<2 & da$RC<= -0.95,]
y1  <- NULL;
for (i in t1){
  tmp0<-nrow(da1[da1$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y1<-rbind(y1, tmp1)
}
y1<-data.frame(y1, "abs(bNTI.ghost) < 2 & RC <= -0.95")
names(y1)<-c("Value", "TP.TREAT", "bNTI.ghost.RC.partition")

da2<-da[abs(da$bNTI.ghost)< 2 & abs(da$RC)< 0.95,]
y2  <- NULL;
for (i in t1){
  tmp0<-nrow(da2[da2$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y2<-rbind(y2, tmp1)
}
y2<-data.frame(y2, "abs(bNTI.ghost) < 2 & abs(RC) < 0.95")
names(y2)<-c("Value", "TP.TREAT", "bNTI.ghost.RC.partition")


da3<-da[abs(da$bNTI.ghost)<2 & da$RC>=0.95,]
y3  <- NULL;
for (i in t1){
  tmp0<-nrow(da3[da3$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y3<-rbind(y3, tmp1)
}
y3<-data.frame(y3, "abs(bNTI.ghost) < 2 & RC >= 0.95")
names(y3)<-c("Value", "TP.TREAT", "bNTI.ghost.RC.partition")

da4<-da[da$bNTI.ghost>=2 & da$RC>=0.95,]
y4  <- NULL;
for (i in t1){
  tmp0<-nrow(da4[da4$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y4<-rbind(y4, tmp1)
}

y4<-data.frame(y4, "bNTI.ghost >= 2 & RC >= 0.95")
names(y4)<-c("Value", "TP.TREAT", "bNTI.ghost.RC.partition")


da5<-da[da$bNTI.ghost>=2 & abs(da$RC)< 0.95,]
y5  <- NULL;
for (i in t1){
  tmp0<-nrow(da5[da5$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y5<-rbind(y5, tmp1)
}

y5<-data.frame(y5, "bNTI.ghost >= 2 & abs(RC) < 0.95")
names(y5)<-c("Value", "TP.TREAT", "bNTI.ghost.RC.partition")


da6<-da[da$bNTI.ghost>=2 & da$RC<= -0.95,]
y6  <- NULL;
for (i in t1){
  tmp0<-nrow(da6[da6$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y6<-rbind(y6, tmp1)
}

y6<-data.frame(y6, "bNTI.ghost >= 2 & RC <= -0.95")
names(y6)<-c("Value", "TP.TREAT", "bNTI.ghost.RC.partition")


#
da7<-da[da$bNTI.ghost<= -2 & da$RC>=0.95,]
y7  <- NULL;
for (i in t1){
  tmp0<-nrow(da7[da7$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y7<-rbind(y7, tmp1)
}

y7<-data.frame(y7, "bNTI.ghost <= -2 & RC >= 0.95")
names(y7)<-c("Value", "TP.TREAT", "bNTI.ghost.RC.partition")


da8<-da[da$bNTI.ghost<= -2 & abs(da$RC)< 0.95,]
y8  <- NULL;
for (i in t1){
  tmp0<-nrow(da8[da8$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y8<-rbind(y8, tmp1)
}

y8<-data.frame(y8, "bNTI.ghost <= -2 & abs(RC) < 0.95")
names(y8)<-c("Value", "TP.TREAT", "bNTI.ghost.RC.partition")


da9<-da[da$bNTI.ghost<= -2 & da$RC<= -0.95,]
y9  <- NULL;
for (i in t1){
  tmp0<-nrow(da9[da9$TP.TREAT== i,])
  tmp1<-data.frame(tmp0,i)
  y9<-rbind(y9, tmp1)
}

y9<-data.frame(y9, "bNTI.ghost <= -2 & RC < -0.95")
names(y9)<-c("Value", "TP.TREAT", "bNTI.ghost.RC.partition")


#y6 <-15 - (y1$Value+y2$Value+y3$Value+y4$Value+y5$Value+y6$Value+y7$Value+y8$Value+y9$Value)
#y6<-data.frame(y6,y1$TP.TREAT, "Others")
#names(y6)<-c("Value", "TP.TREAT", "bNTI.ghost.RC.partition")
bNTI.ghost.RC.part<-rbind(y1,y2,y3,y4,y5, y6, y7, y8,y9)

#bNTI.ghost.RC.part$TP.TREAT
bNTI.ghost.RC.part2<-cSplit(bNTI.ghost.RC.part, "TP.TREAT", ".")
bNTI.ghost.RC.part2$TP.TREAT_1<-as.numeric(gsub("TP", "" , bNTI.ghost.RC.part2$TP.TREAT_1))
bNTI.ghost.RC.part.TP.TREAT<-bNTI.ghost.RC.part2
names(bNTI.ghost.RC.part.TP.TREAT)<-c("Value","bNTI.ghost.RC.partition",  "TP", "Habitat", "Treatment")


#SCNM

source("sncm.fit.R")
#tmp<-read.csv("fungL.R362F.csv", head =T, row.names =1)
d.ck<-data.frame()
for (j in c("Root", "Rhizosphere", "Leaf", "Soil")){
  for (i in c(1:17)){
    tmp0<-tmp[env.L$Treatment1=="Control" & env.L$Habitat== j & env.L$TP== i,]
    dd<-data.frame(sncm.fit(tmp0),j,i, "Control")
    d.ck<-rbind(d.ck, dd)
  }
}


tmp0<-tmp[env.L$Treatment1=="Control" & env.L$Habitat== "Soil" & env.L$TP== 0,]
dd<-data.frame(sncm.fit(tmp0),"Soil", 0 , "Control")
names(dd)<-names(d.ck)
d.ck<-rbind(d.ck, dd)

tmp0<-tmp[env.L$Treatment1=="Pre_flowering_drought" & env.L$Habitat== "Soil" & env.L$TP== 0,]
dd<-data.frame(sncm.fit(tmp0),"Soil", 0 , "Pre_flowering_drought")
names(dd)<-names(d.ck)
d.ck<-rbind(d.ck, dd)

tmp0<-tmp[env.L$Treatment1=="Post_flowering_drought" & env.L$Habitat== "Soil" & env.L$TP== 0,]
dd<-data.frame(sncm.fit(tmp0),"Soil", 0 , "Post_flowering_drought")
names(dd)<-names(d.ck)
d.ck<-rbind(d.ck, dd)

d.pr<-data.frame()
for (j in c("Root", "Rhizosphere", "Leaf", "Soil")){
  for (i in c(3:17)){
    tmp0<-tmp[env.L$Treatment1=="Pre_flowering_drought" & env.L$Habitat== j & env.L$TP== i,]
    dd<-data.frame(sncm.fit(tmp0),j,i, "Pre_flowering_drought")
    d.pr<-rbind(d.pr, dd)
  }
}

d.po<-data.frame()
for (j in c("Root", "Rhizosphere", "Leaf", "Soil")){
  for (i in c(8:17)){
    tmp0<-tmp[env.L$Treatment1=="Post_flowering_drought"& env.L$Habitat== j & env.L$TP== i,]
    dd<-data.frame(sncm.fit(tmp0),j,i, "Post_flowering_drought")
    d.po<-rbind(d.po, dd)
  }
}
names(d.po)<-names(d.pr)<-names(d.ck)
L.sncm<-rbind(d.po,d.pr,d.ck)
#L.sncm$X.Control.
L.sncm$lev<-interaction(L.sncm$j,L.sncm$X.Control.,L.sncm$i,sep = ":")
names(L.sncm)<-c( "m","m.ci","m.mle","maxLL","binoLL","poisLL","Rsqr","Rsqr.bino","Rsqr.pois","RMSE","RMSE.bino","RMSE.pois","AIC","BIC","AIC.bino","BIC.bino","AIC.pois","BIC.pois","N","Samples","Richness","Detect","Habitat", "TP", "Treatment","Level")

t1<-levels(droplevels(env.L$bb))
Fst = NULL
for (i in t1){
  m1<-w.fst(tmp[env.L$bb== i,])
  m1<-data.frame(m1, i)
  Fst<-rbind(Fst,m1)
}
names(Fst)<-c("Fst", "TP.TREAT")

phylo = read.tree("EPICON.fungi.tree.txt");
#phylo; # a summary of the phylogeny
#plot.phylo(phylo,typ="fan", font =1, cex=1)
bNTI.ghost<-read.csv("weighted_bNTI.ghost.F.csv", head = T, row.names =1)
bNTI.ghost<-as.dist(bNTI.ghost)
bNTI.ghost01<-(bNTI.ghost-min(bNTI.ghost))/(max(bNTI.ghost)-min(bNTI.ghost))

#RC
rc0<-read.csv("rc.RSZL.F.csv", head = T, row.names =1)
rc<-as.dist(rc0)
rc01<-(rc+1)/2

env.L$va<-interaction(env.L$TP, env.L$Habitat2)
fd<-beta.pair(tmp01, index.family = "jaccard")
bc<-vegdist(tmp)
bd.rc<-betadisper(rc01,env.L$va)
env.L$RCdisper<-bd.rc$distances
bd.bc<-betadisper(bc,env.L$va)
env.L$bradisper<-bd.bc$distances
bd.jac<-betadisper(fd$beta.jac,env.L$va)
env.L$jacdisper<-bd.jac$distances
bd.jne<-betadisper(fd$beta.jne,env.L$va)
env.L$jnedisper<-bd.jne$distances
bd.jtu<-betadisper(fd$beta.jtu,env.L$va)
env.L$jtudisper<-bd.jtu$distances
bd.bNTI.ghost01<-betadisper(bNTI.ghost01,env.L$va)
env.L$bNTI.ghostdisper<-bd.bNTI.ghost01$distances

##Meta data###
#env.L$Fungi.pct<-rowSums(fungL.rawF)/colSums(fung0.L[,26:277])
env.L$S.raw<-specnumber(fung.raw)
env.L$S.rar362<-specnumber(tmp)
env.L$OTU15_Ustilago<-tmp$OTU15_Ustilago
env.L$yeasts<-tmp$OTU26_Sporobolomyces+tmp$OTU10_Filobasidium+tmp$OTU24_Cryptococcus+tmp$OTU14_Symmetrospora
Laggmeta<-aggregate(cbind(env.L$Fungi.pct, env.L$S.raw, env.L$S.rar362,env.L$RCdisper, 
                          env.L$bradisper, env.L$jacdisper, env.L$jnedisper, 
                          env.L$jtudisper),by=list(env.L$bb) , mean)
names(Laggmeta)<-c("TP.TREAT","Fungi.pct", "S.raw", "S.rar362", "RCdisper", "bradisper",
                   "jacdisper", "jnedisper", "jtudisper")
Lagg<-merge(LaggRC,  Laggmeta, by="TP.TREAT", all = FALSE)
Lagg<-merge(Lagg,  Lagg2bNTI.ghost,  by="TP.TREAT", all = FALSE)
Lagg<-merge(Lagg,  Lagg2bNTI.ghost2RC95pct, by="TP.TREAT", all = FALSE)

fung.L1<-cSplit(Lagg, "TP.TREAT", ".")
fung.L1$TP.TREAT_1<-as.numeric(gsub("TP", "" , fung.L1$TP.TREAT_1))
fung.L1$Level<-interaction(fung.L1$TP.TREAT_2,fung.L1$TP.TREAT_3 ,fung.L1$TP.TREAT_1 ,sep = ":")
Lagg<-data.frame(fung.L1$Level,Lagg)
Lagg<-merge(Lagg, L.sncm, by.x="fung.L1.Level", by.y= "Level", all= TRUE )
#L.sncm$Level
#Lagg$fung.L1.Level
Lagg<-merge(Lagg,Fst, by="TP.TREAT")

## LaggqPCR
env.LqPCR<-env.L[env.L$qPCR > 0, ]
LaggqPCRmeta<-aggregate(cbind(env.LqPCR$Fungi.pct,env.LqPCR$qPCR, env.LqPCR$S.raw, env.LqPCR$S.rar362,
                              env.LqPCR$RCdisper, env.LqPCR$bradisper, env.LqPCR$jacdisper, 
                              env.LqPCR$jnedisper,env.LqPCR$jtudisper),by=list(env.LqPCR$bb) , mean)

names(LaggqPCRmeta)<-c("TP.TREAT","Fungi.pct", "qPCR", "S.raw", "S.rar362", "RCdisper", "bradisper",
                       "jacdisper", "jnedisper", "jtudisper")


LaggqPCR<-merge(LaggRC,  LaggqPCRmeta, by="TP.TREAT", all = FALSE)
LaggqPCR<-merge(LaggqPCR,  Lagg2bNTI.ghost,  by="TP.TREAT", all = FALSE)
LaggqPCR<-merge(LaggqPCR,  Lagg2bNTI.ghost2RC95pct, by="TP.TREAT", all = FALSE)


fung.L1qPCR<-cSplit(LaggqPCR, "TP.TREAT", ".")
fung.L1qPCR$TP.TREAT_1<-as.numeric(gsub("TP", "" , fung.L1qPCR$TP.TREAT_1))
fung.L1qPCR$Level<-interaction(fung.L1qPCR$TP.TREAT_2,fung.L1qPCR$TP.TREAT_3 ,fung.L1qPCR$TP.TREAT_1 ,sep = ":")
LaggqPCR<-data.frame(fung.L1qPCR$Level,LaggqPCR)
LaggqPCR<-merge(LaggqPCR, L.sncm, by.x="fung.L1qPCR.Level", by.y= "Level", all= TRUE )

LaggqPCR<-merge(LaggqPCR,Fst, by="TP.TREAT")

##Meta data Transcriptome###

LaggmetaMet<-aggregate(cbind(env.Tra$Pct.Tra, 
                             env.Tra$S.rar362,env.Tra$RCdisper, env.Tra$bradisper,
                             env.Tra$jacdisper, env.Tra$jnedisper, 
                             env.Tra$jtudisper),by=list(env.Tra$bb) , mean)
names(LaggmetaMet)<-c("TP.TREAT","Fungi.pct.tra", "S.rar362", "RCdisper", "bradisper",
                      "jacdisper", "jnedisper", "jtudisper")
Traagg<-merge(LaggRC, LaggmetaMet, by="TP.TREAT", all = FALSE)
Traagg<-merge(Traagg,  Lagg2bNTI.ghost, by="TP.TREAT", all = FALSE)
Traagg<-merge(Traagg,  Lagg2bNTI.ghost2RC95pct, by="TP.TREAT", all = FALSE)
fung.L1<-cSplit(Traagg, "TP.TREAT", ".")
fung.L1$TP.TREAT_1<-as.numeric(gsub("TP", "" , fung.L1$TP.TREAT_1))
#fung.L1$Level<-interaction(fung.L1$TP.TREAT_2,fung.L1$TP.TREAT_1 ,sep = ":")
fung.L1$Level<-interaction(fung.L1$TP.TREAT_2,fung.L1$TP.TREAT_3 ,fung.L1$TP.TREAT_1 ,sep = ":")
Traagg<-data.frame(fung.L1$Level,Traagg)
Traagg<-merge(Traagg, L.sncm, by.x="fung.L1.Level", by.y= "Level", all= FALSE )
Traagg<-merge(Traagg,Fst, by="TP.TREAT")



save.image("EPICON.data.preparation.RC.bNTI.ghost.2019.03.17.Rdata")